---
name: "Andrés F. Quintero"
position: "Software Developer"
phone: +57 301 435 700
email: "afquinteromoreano@gmail.com"
github: andyquinterom
linkedin: andresquinterom
profilepic: "perfil.jpeg"
date: "`r format(Sys.time(), '%m %Y')`"
aboutme: "I a software developer from Colombia and an R enthusiast. I love building tools and sharing them with the community."
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About Me

-   App and library developer.
-   R Shiny expert.
-   Advanced GNU/Linux user.
-   Expert in Healthcare Contracting in Colombia.
-   Native spanish speaker

# Programming Languages

-  R (+ Shiny)
-  JavaScript
-  Java
-  SQL
-  Bash/Sh

# Technologies

-  GNU/Linux (Debian/ Arch/ RedHat)
-  PostgreSQL
-  NGINX
-  NodeJS
-  Amazon Web Services
-  Microsoft Azure
-  Vim
-  Docker

# Projects and contributions

```{r}
library(tibble)
tribble(
  ~ Nombre, ~ Year, ~ Enlace,
  "Analítica Integrada Salud", "2019-2021", "https://github.com/proyais/aisalud",
  "YouTube Channel", "2020-2021", "https://bit.ly/39th3op",
  "ComBD", "2019-2021", "https://github.com/proyais/aisalud_combd",
  "shinyCache", "2021", "https://github.com/proyais/shinyCache",
  "DBPlyr", "2021", "https://github.com/tidyverse/dbplyr",
  "RSConnect", "2021", "https://github.com/rstudio/rsconnect"
) %>% 
  detailed_entries(Nombre, Year, Enlace)
```

# Experience

```{r}
library(tibble)
tribble(
  ~ what, ~ when, ~with,
  "Developer and Consultant", "2019-2021", "MD&CO Consulting Group",
  "Developer", "2020", "p4s Hackathon Covid-19"
) %>% 
  detailed_entries(what = what, when = when, with = with)
```

# Education

```{r}
library(tibble)
tribble(
  ~when, ~with, ~why, 
  "2006-2020", "Colegio Bolivar (Cali)", list("Academic excellence",
                                              "Best Senior Project",
                                              "Honor society"),
  "2020", "University of Chicago", "Micro-economics"
) %>% 
  detailed_entries(when = when, with = with, why = why)
```
